---
title: "TidyTemplate"
date: 2022-11-08
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(scales)
library(lubridate)
theme_set(theme_light())

```

# Load the weekly Data

```{r Load}

tt <- tt_load("2022-11-01")
horror_movies <- tt$horror_movies

horror_movies %>% 
    mutate(year = year(release_date), sort = TRUE) %>% 
    ggplot(aes(year)) +
    geom_histogram()

horror_movies %>% 
    dplyr::filter(runtime > 60, runtime <= 300) %>% 
    ggplot(aes(runtime)) +
    geom_histogram() +
    scale_x_log10()
```



# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}



```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}


  
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "My TidyTuesday Plot.png",
  device = "png")

```
