```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}

```

```{r pressure, echo=FALSE}
library(tidyverse)
library(scales)
theme_set(theme_light())
```

```{r echo=FALSE}
recent_grads <- read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/recent-grads.csv")

# first data cleaning
major_processed <- recent_grads %>%
    arrange(desc(Median)) %>% 
    mutate(Major = str_to_title(Major), # converts uppercased characters to titlecased
           Major = fct_reorder(Major, Median)) 
```

1:01:25: Create ShareWomen variable

```{r}
by_major_categry <- major_processed %>%
    filter(!is.na(Total)) %>% 
    group_by(Major_category) %>%
    summarise(Men = sum(Men),
              Women = sum(Women),
              Total = sum(Total),
              # weight medians by SampleSize
              MedianSalary = sum(Median * Sample_size / sum(Sample_size))) %>%
    mutate(ShareWomen = Women / Total) %>% 
    arrange(desc(ShareWomen))
```

### Gender shares in most common majors (32min)

```{r echo=FALSE}
# show categories with highest major's 
by_major_categry %>% 
    mutate(Major_category = fct_reorder(Major_category, Total)) %>% 
    gather(Gender, Number, Men, Women) %>% 
    View()
    ggplot(aes(Major_category, Total, fill = Gender)) +
    geom_col() +
    coord_flip() +
    labs(x = "",
         y = "Total number of graduates")
```

# What are the highest earning majors?

```{r echo=FALSE}
major_processed %>% 
    filter(Sample_size >= 100) %>% 
    head(10) %>% 
    ggplot(aes(Major, Median, color = Major_category)) +
    geom_point() +
    geom_errorbar(aes(ymin = P25th, ymax = P75th)) +
    expand_limits(y = 0) +
    scale_y_continuous(labels = dollar_format()) +
    coord_flip() +
    labs(title = "What are the highest-earning majors",
         subtitle = "Top 20 majors with at lease 100 graduades surveyed",
         x = "",
         y = "Median salary of graduades")
```

```{r echo=FALSE}
major_processed %>% 
    mutate(Major_category = fct_reorder(Major_category, Median)) %>% 
    ggplot(aes(Major_category, Median)) +
    geom_boxplot() +
    scale_y_continuous(labels = dollar_format()) +
    coord_flip()
```

```{r echo=FALSE}
major_processed %>% 
    mutate(Major_category = fct_reorder(Major_category, Median)) %>% 
    group_by(Major_category) %>% 
    summarise(Median = median(Median)) %>% 
    ggplot(aes(Major_category, Median)) +
    geom_col() +
    scale_y_continuous(labels = dollar_format()) +
    coord_flip()
```

What are the hightest Majors?

```{r echo=FALSE}
major_processed %>% 
    head(20) %>% 
    ggplot(aes(Major, Median, color = Major_category)) +
    expand_limits(y = 0) +
    geom_point() +
    geom_errorbar(aes(ymin = P25th, ymax = P75th)) +
    scale_y_continuous(labels = dollar_format()) +
    coord_flip()
```

What are the lowest majors?

```{r echo=FALSE}
major_processed %>% 
    tail(20) %>% 
    ggplot(aes(Major, Median, color = Major_category)) +
    expand_limits(y = 0) +
    geom_point() +
    geom_errorbar(aes(ymin = P25th, ymax = P75th)) +
    scale_y_continuous(labels = dollar_format()) +
    coord_flip()
```

### How does gender breakdown relate to typical earnings? (36 min)

```{r}
major_processed %>% 
    arrange(desc(Total)) %>% # will display top Majors by the count of people
    head(20) %>% 
    mutate(Major = fct_reorder(Major, Total)) %>% 
    gather(Gender, Number, Men, Women) %>% 
    select(Major, Gender, Number) %>% 
    ggplot(aes(Major, Number, fill = Gender)) +
    geom_col() +
    coord_flip() +
    scale_y_continuous(labels = comma_format())
```


```{r}
library(ggrepel)

by_major_categry %>% 
    ggplot(aes(ShareWomen, MedianSalary)) +
    geom_point() +
    # cave: Engeneering and Math are outliers in two dimensions (High Salary and more Men)
    geom_smooth(method = "lm") +
    geom_text_repel(aes(label = Major_category), force = .2) +
    expand_limits(y = 0)
```

Salary and Women by Major (expressed in the Median column) (48 min)

```{r}
library(ggrepel)

# for doing a statistical test we should be careful if aggregating first
# This will reduce statistical power and hide some of the variation in the data
# also be awere of simpson paradox (some Major_categories with high women percentage)
# will have high Salaries, excluding those would potentially change the direction of the correlation
major_processed %>% 
    ggplot(aes(ShareWomen, Median, color = Major_category)) +
    geom_point() +
    # cave: Engeneering and Math are outliers in two dimensions (High Salary and more Men)
    # group aes argument to make lm for all categories
    geom_smooth(aes(group = 1), method = "lm") +
    expand_limits(y = 0)
```

Weighted (on Sample_size) linear regression to predict Median salary from ShareWomen 51 nin
wLR expects a Mean, but salary data is log normally distributed, the median is close geometric mean
Estimate: if you would go from 0 % to 100 % women

```{r}
major_processed %>% 
   select(Major, Total, ShareWomen, Sample_size, Median) %>% 
    lm(Median ~ ShareWomen, data = ., weights = Sample_size) %>% 
    summary()
```

Detect correlations with salary within Major_category with  is 54 min

```{r}
library(broom)

major_processed %>% 
    select(Major, Major_category, Total, ShareWomen, Sample_size, Median) %>% 
    add_count(Major_category) %>% # will add an extra column with counts of distinct categories
    filter(n >= 10) %>% 
    nest(-Major_category) %>% 
    # within every Major category "Median explained by ShareWomen on this data with these weights"
    mutate(model = map(data, ~lm(Median ~ ShareWomen, data = ., weights = Sample_size)),
           tidied = map(model, tidy)) %>% 
    unnest(tidied) %>% 
    filter(term == "ShareWomen") %>% 
    arrange(estimate) %>% 
    # adjusting p-value not by multiplying by the category count
    # instead using false discovery rate
    # if there is a significant correlation we would be 10% wrong in those categories with the smallest fdr
    # linear effects model would be more appropriate to use here
    # in those 4 groups the data suggests there is negative correlation within departments and not just across them
    mutate(fdr = p.adjust(p.value, method = "fdr"))
```
