```{r}
library(tidyverse)
library(janitor)
library(scales)
library(lubridate)
library(countrycode)

theme_set(theme_light())

RD_year_2023 <- read_csv2("~/Desktop/gab_2023_rettungsdiensteinsaetze.csv", 
                         locale = locale(encoding = "latin1"))

# package downloads (50:00)
package_downloads <- read_csv("http://cran-logs.rstudio.com/2024/2024-08-22.csv.gz")

r_downloads_year <- r_downloads_year %>% 
    select(-"...1") %>% 
    mutate(weekday = wday(date, label = TRUE),
           country = countrycode(country, "iso2c", "country.name"))
```

5:00 Look at downloads over time

```{r}
r_downloads_year %>% 
    count(date) %>% 
    ggplot(aes(date, n)) +
    geom_line() +
    expand_limits(y = 0) +
    labs(y = "R downloads")
```

9:00 Look at downloads in a week (averages)

```{r}
# this is a biggy!
# cool way to display weekdays
# and group arguments in geom_line (not sure what group argument does)
# AAAAAND mutate thinge inside group_by method is so coool!!!
r_downloads_year %>% 
    count(date) %>% 
    # there will be a lot data for every weekday
    group_by(weekday = wday(date, label = TRUE)) %>% 
    mutate(average = mean(n)) %>% 
    ggplot(aes(weekday, average)) +
    geom_line(group = 1) +
    expand_limits(y = 0)

# trying to understand the group argument in geom_line
test <- r_downloads_year %>% 
    count(date) %>% 
    group_by(weekday = wday(date, label = TRUE)) %>% 
    mutate(average_dwn_wday = mean(n)) 
```

10:00 Change of R downloads over week

```{r}
r_downloads_year %>% 
    count(week = floor_date(date, "week")) %>% 
    # remove incomplete weeks
    filter(week > min(week)) %>% 
    ggplot(aes(week, n)) +
    geom_line() +
    expand_limits(y = 0) +
    labs(y = "downlads per week")
```

12:00 Change country abbreviation to country name

```{r}
r_downloads_year %>% 
    count(country = countrycode(country, "iso2c", "country.name"), sort = TRUE) %>% 
    filter(!is.na(country)) %>% 
    mutate(percent = n / sum(n)) %>% 
    head(16) %>% 
    mutate(country = fct_reorder(country, percent)) %>% 
    ggplot(aes(country, percent)) +
    geom_col() +
    coord_flip() +
    scale_y_continuous(labels = percent_format()) +
    labs(title = "What countries install the most R")
```

17:00 Line graph for versions over time

```{r}
r_downloads_year %>% 
    # only 7 most used, the rest will be other
    mutate(version = fct_lump(version, 7)) %>% 
    count(date, version) %>% 
    ggplot(aes(date, n, color = version)) +
    geom_line()
```

22:00 R installation over time of day

```{r}
r_downloads_year %>% 
    filter(!is.na(country)) %>% 
    count(hour = hour(time),
          country = fct_lump(country, 8)) %>% 
    ggplot(aes(hour, n)) +
    geom_line() +
    expand_limits(y = 0) +
    facet_wrap(~ country, scales = "free_y")
```

29:00 Line graph for downloads over time based on country

```{r}
r_downloads_year %>% 
    count(country = fct_lump(country, 8),
          week = floor_date(date, "week")) %>%
    # first week is incomplete, filter it
    filter(week >= min(week)) %>%
    ggplot(aes(week, n, color = country)) +
    geom_line()
               
```

33:00 IP Adress saga (takes long to calculate and run!)

```{r}
r_downloads_year %>% 
    count(ip_id, sort = TRUE) %>% 
    ggplot(aes(n)) +
    geom_histogram()

r_downloads_gaps <- r_downloads_year %>% 
    mutate(datetime = as.POSIXct(date) + time) %>% 
    arrange(datetime) %>% 
    group_by(ip_id) %>% 
    mutate(gap = as.numeric(datetime - lag(datetime))) %>% 
    filter(!is.na(gap))

r_downloads_gaps %>% 
    count(country, gap) %>% 
    # filter(country == "United States") %>% 
    ggplot(aes(gap)) +
    geom_histogram() +
    geom_vline(color = "red", lty = 2, xintercept = 86400) +
    # clear bimodal log normal distribution
    # scale_x_log10()
    scale_x_log10(breaks = 60 ^ (0:4),
                  labels = c("Second", "Minute", "Hour", "2.5 Days", "120 Days"))
    
```

42:00 Downloads per weeek (distinct IP adresses

```{r}
r_downloads_year %>% 
    group_by(week = floor_date(date, "week")) %>%
    summarise(n = n_distinct(ip_id)) %>% 
    # first week is incomplete, filter it
    filter(week >= min(week)) %>%
    ggplot(aes(week, n)) +
    geom_line() +
    expand_limits(y = 0) +
    labs(y = "Downloads per weeek (distinct IP adresses")
```

# 50:00 R package downloads in different countries

```{r}
package_downloads %>% 
    filter(country %in% c("US", "IN")) %>% 
    group_by(country, package) %>%
    summarise(n = n_distinct(ip_id)) %>%
    # missing values (NA) will be replaced by 0 (fill argument)
    spread(country, n, fill = 0) %>% 
    # no ungrouping needed, not sure why
    ungroup() %>%
    mutate(total = US + IN,
           # Laplace smothing: prevents Infitity in rations 
           # Inf rations will result because of zero division  US / IN == 0
           IN = (IN + 1) / (sum(IN) + 1),
           US = (US + 1) / (sum(US) + 1),
           ratio = US / IN) %>% 
    filter(total >= 1000) %>% 
    arrange(desc(ratio))
```
