```{r}
library(tidyverse)
library(scales)
theme_set(theme_classic())

thanksgiving_survey <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/refs/heads/main/data/2018/2018-11-20/thanksgiving_meals.csv")
```

```{r}
thanksgiving_survey %>% 
    count(celebrate)

# give me some gravy
thanksgiving_survey %>%
    count(main_dish, main_prep, sort = TRUE)
```

11:00 Income

```{r}
thanksgiving_survey %>% 
    mutate(family_income = parse_number(family_income)) %>% 
    filter(cranberry %in% c("Homemade", "Canned")) %>% 
    group_by(family_income) %>% 
    summarize(homemade = sum(cranberry == "Homemade"),
              total = n(),
              low = qbeta(0.025, homemade + .5, total - homemade + .5),
              high = qbeta(0.975, homemade + .5, total - homemade + .5)) %>% 
    ggplot(aes(family_income, homemade / total, group = 1)) +
    geom_line() +
    geom_ribbon(aes(ymin = low, ymax = high), alpha = .2) + 
    scale_y_continuous(labels = scales::percent_format()) +
    geom_smooth() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
 ```
```

20:00 Celebrate

```{r}
thanksgiving_survey %>% 
    group_by(family_income) %>% 
    summarize(celebrate = sum(celebrate == "Yes"),
              total = n(),
              low = qbeta(0.025, celebrate + .5, total - celebrate + .5),
              high = qbeta(0.975, celebrate + .5, total - celebrate + .5)) %>% 
    ggplot(aes(family_income, celebrate / total, group = 1)) +
    geom_line() +
    geom_ribbon(aes(ymin = low, ymax = high), alpha = .2) + 
    scale_y_continuous(labels = scales::percent_format()) +
    geom_smooth() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

23:00

```{r}
food_gathered <- thanksgiving_survey %>% 
    select(id, starts_with("side"),
           starts_with("pie"),
           starts_with("dessert")) %>% 
    select(-side15, -pie13, -dessert12) %>% 
    gather(type, value, -id) %>% 
    filter(!is.na(value),
           !value %in% c("None", "Other (please specify)")) %>% 
    mutate(type = str_remove(type, "\\d+"))
```

28:00

```{r}
food_gathered %>% 
    count(type, value, sort = TRUE) %>% 
    mutate(value = fct_reorder(value, n)) %>% 
    ggplot(aes(value, n, fill = type)) +
    geom_col(show.legend = FALSE) +
    coord_flip() +
    facet_wrap(~type, ncol = 1, scales = "free_y")
```

36:00 - Food by size of country

```{r}
food_gathered %>% 
    inner_join(thanksgiving_survey, by = "id") %>% 
    group_by(us_region) %>% 
    mutate(respondents = n_distinct(id)) %>% 
    count(us_region, respondents, type, value) %>% 
    ungroup() %>% 
    mutate(percent = n / respondents)
    
    
```

